### 2018-09-04 doc/plos/text/manuscript.tex
add abscission experiments
and some small wording tweaks

In all instances, the nowcast has lower error (both MAE and RMSE) than any
individual data source, subject to the fitting procedure described above. This
indicates, at least for the US as a whole, that the nowcast is on average more
accurate than any individual data source.

@@

As expected, we generally find that removal of a particular data source causes
an increase (or, in the case of WIKI, no meaningful change) in nowcasting
error. However, there are a couple of exceptions: TWTR and CDC. Nowcasting
error \textit{decreases} when removing these data sources. This is unexpected
in theory and strongly suggests violated assumptions (e.g. the relationship of
these sources with wILI may be nonlinear) or overfitting (e.g. covariance may
be underestimated for these sources).

@@

TODO(abscission experiments)

@@

\paragraph*{S1 Text}
\label{S1_Text}
{\bf Supporting Information.} Includes derivation and sensitivity analysis.

>>>>

In all instances, the nowcast has lower error (both MAE and RMSE) than any
individual data source after applying the fitting procedure described above. This
indicates, at least for the US as a whole, that the nowcast is on average more
accurate than any individual data source (at least for this particular fitting
procedure).

@@

As expected, we generally find that removal of a particular data source causes
an increase (or, in the case of WIKI, no meaningful change) in nowcasting
error. However, there are a couple of exceptions: TWTR and CDC. Nowcasting
error \textit{decreases} when removing these data sources. This is unexpected
in theory and strongly suggests violated assumptions (e.g. the relationship of
these sources with wILI may be nonlinear or residuals may not be normally
distributed) or overfitting (e.g. covariance may be underestimated for these
sources) in practice.

@@

A related question is to what extent the inclusion of geographic ``tiers''
impacts accuracy of nowcasts. Namely, is it helpful for nowcasting the US
nationally to include data at the level of regions, states, cities, and
territories?

To answer this, we similarly compare nowcasting error in terms of MAE and RMSE
with and without data at regional (Census and HHS) and state (including cities
and territories) levels. This is difficult to assess for all data sources,
given that many do not include data at the level of states (or even regions, in
the case of WIKI). Because of this, we limit the set of data sources to only
those available at the level of states (and above): GFT, GHT, TWTR, CDCP, and
SAR3. Again, we restrict the comparison to weeks on which sensors are mutually
available. The results of these comparisons are summarized in
Fig~\ref{figure_accuracy_vs_abscission}.

\begin{figure}[!ht]
  \maybeincludegraphics{accuracy_vs_abscission}
  \caption{
    {\bf Nowcast error compared across geographic tiers.}
    TODO: explain this
  }
  \label{figure_accuracy_vs_abscission}
\end{figure}

Between national-only and national-and-regional nowcasts, we see an increase in
accuracy (a decrease in both MAE and RMSE), suggesting that higher geographic
resolution is beneficial to the nowcast. When including all locations, MAE
further decreases, but RMSE increases. One possible reason for this mixed
result is poor model fitting (i.e. covariance estimation) induced by a large
increase in dimensionality with no increase in the number of weekly sensor
observations.

@@

\paragraph*{S1 Text}
\label{S1_Text}
{\bf Supporting Information.} Derivation of the sensor fusion kernel.
